---
title: "Coursera Data Product Project"
author: "Frank Hasbani PMP, CSM"
framework: io2012
output: html_document
hitheme: tomorrow
job: Student at Johns Hopkins 
knit: slidify::knit2slides
logo: lib:../libraries assets:../assets
mode: selfcontained
highlighter: highlight.js
subtitle: The Data Explorer
ext_widgets:
  rCharts: libraries/nvd3
widgets:
- bootstrap
- quiz
- shiny
- interactive
- mathjax
---

## Summary

Ever wonder if your car's MPG you are currently driving is above or below average?
Are you evaluating a new car and would like to find out if it is delivering a good MPG?

Wonder no more. The Car Mileage Predictor is based on a predictive model conducted using public records of 32 cars of diverse makes and models.
The Car Mileage Predictor is a calculator of Miles Per Gallon (MPG) of a hypothetical car based on the Weight(wt), Quarter Of A Mile in Seconds(qsec) and if the Transmission is Automatic or Manual.

- First enter the weight of your car in lbs.

- Second enter the number of seconds for the car to reach quarter of a mile

- Last check if the transmission is manual or leave unchecked for automatic

The Predictive Model and analysis are available for scrutiny at: https://fhasbani.shinyapps.io/MPG-Predictor-Data-Product


--- .class #id 

## Analysis of the Model 
The Predictor Model Coefficients are:
```{r, echo=FALSE}

model <- lm(mpg ~ wt + am + qsec, data = mtcars)
summary(model)$coefficients
```   
The multiple R squared is `r summary(model)$r.squared`, adjusted R Squared is `r summary(model)$adj.r.squared` and F-STatistic is `r summary(model)$fstatistic`


--- .class #id 

## Exploratory Data Analysis


```{r, echo=FALSE}
plot(mtcars)
```

---
## How to use the Predictor
- Predictor Tab is reactive to the 3 predictor variables in the SideBar Panel on the left side. Feel free to change any of the variable and see results.
- How to Use It: Explains how to effectively use and understand this tool 
- Raw Data Tab: Shows the source data used to build the prediction model in a Table format
- Structure Tab: Shows the structure of the same data
- Summary Tab: Shows the summary of both the Model and the Data, and explains the effectivness of the model.
- Box Plot Tab: Shows a Box Plot of the Variances of the MPG based of the number of cylinders
- Correlation Plot Tab: Shows the Correlation between all the Column Variables
